### 2022-05-28 paper/localpsf.tex
editing pass on computational cost section

\paragraph{(2): H-matrix operations} H-matrix methods for matrix-vector products, matrix-matrix addition, matrix-matrix multiplication, matrix factorization, and matrix inversion require
\begin{equation*}
	O(k_h^2 N \log(N)^a) \qquad \text{work},
\end{equation*}
where $a \in \{0,1,2,3\}$. The precise cost depends on the type of H-matrix used and the operation being performed; for more details see \cite{GrasedyckHackbusch03}. The rational method for modifying $\mathbf{A}_H$ to be positive semi-definite, described in Appendix \ref{sec:make_spd}, is performed using two matrix-matrix additions, $l+1$ matrix-matrix multiplications, and one matrix inversion, where $2^l$ is the order of the rational function used.

>>>>

\paragraph{(3): H-matrix operations} H-matrix methods for matrix-vector products, matrix-matrix addition, matrix-matrix multiplication, matrix factorization, and matrix inversion require
\begin{equation*}
	O(k_h^2 N \log(N)^a) \qquad \text{work},
\end{equation*}
where $a \in \{0,1,2,3\}$. The precise cost depends on the type of H-matrix used and the operation being performed; for more details see \cite{GrasedyckHackbusch03}. The rational method for modifying $\mathbf{A}_H$ to be positive semi-definite, described in Appendix \ref{sec:make_spd}, is performed using two matrix-matrix additions, $l+1$ matrix-matrix multiplications, and one matrix inversion, where $2^l$ is the order of the rational function used.
